### 2024-12-19 README.Rmd
update codecov thing

<!-- badges: start -->
[![traveltime status badge](https://idem-lab.r-universe.dev/badges/traveltime)](https://idem-lab.r-universe.dev/traveltime)
[![R-CMD-check](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/idem-lab/traveltime/branch/main/graph/badge.svg)](https://app.codecov.io/gh/idem-lab/traveltime?branch=main)
![GitHub License](https://img.shields.io/github/license/geryan/traveltime)
[![Lifecycle:](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
![GitHub commit activity](https://img.shields.io/github/commit-activity/w/geryan/traveltime)
![GitHub Downloads (all assets, all releases)](https://img.shields.io/github/downloads/geryan/traveltime/total)
![GitHub last commit](https://img.shields.io/github/last-commit/geryan/traveltime)
![GitHub commits since latest release](https://img.shields.io/github/commits-since/geryan/traveltime/latest)
<!-- badges: end -->

@@

*D. J. Weiss, A. Nelson, C. A. Vargas-Ruiz, K. Gligoric, S., Bavadekar, E.
Gabrilovich, A. Bertozzi-Villa, J. Rozier, H. S. Gibson, T., Shekel, C. Kamath,
A. Lieber, K. Schulman, Y. Shao, V. Qarkaxhija, A. K. Nandi, S. H. Keddie, S.
Rumisha, P. Amratia, R. Arambepola, E. G. Chestnutt, J. J. Millar, T. L. Symons,
E. Cameron, K. E. Battle, S. Bhatt, and P. W. Gething.* **Global maps of travel
time to healthcare facilities.** (2020) Nature Medicine.
https://doi.org/10.1038/s41591-020-1059-1

*D. J. Weiss, A. Nelson, H.S. Gibson, W. Temperley, S. Peedell, A. Lieber, M.
Hancher, E. Poyart, S. Belchior, N. Fullman, B. Mappin, U. Dalrymple, J. Rozier,
T.C.D. Lucas, R.E. Howes, L.S. Tusting, S.Y. Kang, E. Cameron, D. Bisanzio, K.E.
Battle, S. Bhatt, and P.W. Gething.* **A global map of travel time to cities to
assess inequalities in accessibility in 2015.** (2018). Nature.
doi:10.1038/nature25181.

>>>>

<!-- badges: start -->
[![traveltime status badge](https://idem-lab.r-universe.dev/badges/traveltime)](https://idem-lab.r-universe.dev/traveltime)
[![R-CMD-check](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml)
![GitHub License](https://img.shields.io/github/license/geryan/traveltime)
[![Lifecycle:](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
![GitHub commit activity](https://img.shields.io/github/commit-activity/w/geryan/traveltime)
![GitHub Downloads (all assets, all releases)](https://img.shields.io/github/downloads/geryan/traveltime/total)
![GitHub last commit](https://img.shields.io/github/last-commit/geryan/traveltime)
![GitHub commits since latest release](https://img.shields.io/github/commits-since/geryan/traveltime/latest)
[![Codecov test coverage](https://codecov.io/gh/idem-lab/traveltime/graph/badge.svg)](https://app.codecov.io/gh/idem-lab/traveltime)
<!-- badges: end -->

@@

*D. J. Weiss, A. Nelson, C. A. Vargas-Ruiz, K. Gligoric, S., Bavadekar, E.
Gabrilovich, A. Bertozzi-Villa, J. Rozier, H. S. Gibson, T., Shekel, C. Kamath,
A. Lieber, K. Schulman, Y. Shao, V. Qarkaxhija, A. K. Nandi, S. H. Keddie, S.
Rumisha, P. Amratia, R. Arambepola, E. G. Chestnutt, J. J. Millar, T. L. Symons,
E. Cameron, K. E. Battle, S. Bhatt, and P. W. Gething.* **Global maps of travel
time to healthcare facilities.** (2020) Nature Medicine.
<https://doi.org/10.1038/s41591-020-1059-1>

*D. J. Weiss, A. Nelson, H.S. Gibson, W. Temperley, S. Peedell, A. Lieber, M.
Hancher, E. Poyart, S. Belchior, N. Fullman, B. Mappin, U. Dalrymple, J. Rozier,
T.C.D. Lucas, R.E. Howes, L.S. Tusting, S.Y. Kang, E. Cameron, D. Bisanzio, K.E.
Battle, S. Bhatt, and P.W. Gething.* **A global map of travel time to cities to
assess inequalities in accessibility in 2015.** (2018). Nature.
<https://doi.org/10.1038/nature25181>
